### 2016-06-29 publications/Journal/1-introduction.tex
Fixed figures for twocolumn

%Usage of Hyperref with hardcoded label is hardly ideal, but ~\ref doesn't work if the layout disables numbered sections, so a hack is needed. The alternative is \nameref but that isn't all that readable.
The remainder of this paper is organized as follows:
Section \hyperref[sec:2-background]{2} introduces the necessary background on synchronization protocols.
Section~\hyperref[sec:3-features]{3} elaborates on our design that enables this flexibility.
In Section~\hyperref[sec:4-performance]{4}, we evaluate performance of our tool by comparing its different synchronization protocols, and by comparing to adevs.
Related work is discussed in Section~\hyperref[sec:5-related-work]{5}.
Section~\hyperref[sec:6-conclusion]{6} concludes the paper and gives future work.

>>>>

%Usage of Hyperref with hardcoded label is hardly ideal, but ~\ref doesn't work if the layout disables numbered sections, so a hack is needed. The alternative is \nameref but that isn't all that readable.
The remainder of this paper is organized as follows:
Section~\hyperref[sec:2-background]{2} introduces the necessary background on synchronization protocols.
Section~\hyperref[sec:3-features]{3} elaborates on our design that enables this flexibility.
In Section~\hyperref[sec:4-performance]{4}, we evaluate performance of our tool by comparing its different synchronization protocols, and by comparing to adevs.
Related work is discussed in Section~\hyperref[sec:5-related-work]{5}.
Section~\hyperref[sec:6-conclusion]{6} concludes the paper and gives future work.

### 2016-06-29 publications/Journal/3-features.tex
Change rng plot.
Signed-off-by: Ben Cardoen <bencardoen@gmail.com>
Fixed figures for twocolumn

\begin{figure}
    \includegraphics[width=\columnwidth]{fig/cores_class_diagram.eps}
	\caption{Dxex design.}
	\label{fig:class_diagram}
\end{figure}

@@

\subsubsection{Memory Management}
\label{sec:4-subsec:overhead-pgraph:memory}
\begin{figure}
    \center
    \includegraphics[width=\modelfraction\columnwidth]{fig/memory_allocators_parallel.eps}
    \caption{Effect of memory allocators on parallel execution time.}
    \label{fig:memallocators_parallel}
\end{figure}
Memory management is traditionally seen as one of the major bottlenecks in parallel computation~\cite{WhatEveryComputerProgrammerShouldKnowAboutMemory}: memory bandwidth doesn't increase as fast as the number of cores using it.
While this is always a problem, it is aggravated in dxex by providing automatic memory management for events and states.
A model written for a sequential simulation will run correctly in a conservative or optimistic simulation without altering (from the point of view of the model author) the (de)allocation semantics of events or states.

@@

\begin{figure}
    \center
    %TODO remove adevs results as not applicable here
    \includegraphics[width=\modelfraction\columnwidth]{fig/rngspeedupeffectdevstone.eps}
    \caption{Speedup with different RNG usage patterns.}
    \label{fig:Queuerngspeedup}
\end{figure}

>>>>

\begin{figure*}
    \includegraphics[width=\textwidth]{fig/cores_class_diagram.eps}
	\caption{Dxex design.}
	\label{fig:class_diagram}
\end{figure*}

@@

\subsubsection{Memory Management}
\label{sec:4-subsec:overhead-pgraph:memory}
\begin{figure}
    \center
    \includegraphics[width=\columnwidth]{fig/memory_allocators_parallel.eps}
    \caption{Effect of memory allocators on parallel execution time.}
    \label{fig:memallocators_parallel}
\end{figure}
Memory management is traditionally seen as one of the major bottlenecks in parallel computation~\cite{WhatEveryComputerProgrammerShouldKnowAboutMemory}: memory bandwidth doesn't increase as fast as the number of cores using it.
While this is always a problem, it is aggravated in dxex by providing automatic memory management for events and states.
A model written for a sequential simulation will run correctly in a conservative or optimistic simulation without altering (from the point of view of the model author) the (de)allocation semantics of events or states.

@@

\begin{figure}
    \center
    \includegraphics[width=\columnwidth]{fig/rngspeedupeffectdevstone.eps}
    \caption{Speedup with different RNG usage patterns compared to STL random number generator.}
    \label{fig:Queuerngspeedup}
\end{figure}

### 2016-06-29 publications/Journal/4a-allocation.tex
Removed "Linking back" subsection
Fixed figures for twocolumn

\begin{figure}
    \center
    \includegraphics[width=\modelfraction\columnwidth]{fig/pholdtree.pdf}
    %TODO depth 1 but 3 levels deep?
    \caption{PHOLDTree model for depth 1 and width 2.}
    \label{fig:PHOLDTree_model}
\end{figure}

@@

\begin{figure}
    \center
    \includegraphics[width=\plotfraction\columnwidth]{fig/pholdtree_sequential_dn.eps}
    \caption{Effect of hierarchy in sequential simulation.}
    \label{fig:PHoldtree_seq_dn_benchmark}
\end{figure}

@@

   \includegraphics[width=\textwidth]{fig/pholdtree_alloc_BF.pdf}
   \caption{PholdTree model breadth first allocation with 4 kernels.}
   \label{fig:PholdTree_model_bfs}
   \includegraphics[width=\textwidth]{fig/pholdtree_alloc_DF.pdf}
   \caption{PholdTree model depth first allocation with 4 kernels.}
   \label{fig:PholdTree_model_dfs}
\end{figure}

@@

\begin{figure}
    \center
    \begin{minipage}{0.45\textwidth}
            \center
            \includegraphics[width=\textwidth]{fig/pholdtreed1n3t5000c4BFS.eps}
            \caption{Visualization of a PholdTree simulation with breadth first allocation and 4 kernels.}
            \label{fig:pholdtree_visualize_parBFS}
    \end{minipage}
    \begin{minipage}{0.45\textwidth}
            \center
            \includegraphics[width=\textwidth]{fig/pholdtreed1n3t5000c4DFS.eps}
            \caption{Visualization of a PholdTree simulation with depth first allocation and 4 kernels.}
            \label{fig:pholdtree_visualize_parDFS}
    \end{minipage}
\end{figure}

@@

\begin{figure}
    \center
    \includegraphics[width=\modelfraction\columnwidth]{fig/pholdtreeallochighp.eps}
    \caption{PholdTree model performance using different allocation schemes.}
    \label{fig:PholdTree_plot_alloc_high}
\end{figure}

\subsection{Linking Back}
%TODO link back to initial performance evaluation

>>>>

\begin{figure}
    \center
    \includegraphics[width=\columnwidth]{fig/pholdtree.pdf}
    %TODO depth 1 but 3 levels deep?
    \caption{PHOLDTree model for depth 1 and width 2.}
    \label{fig:PHOLDTree_model}
\end{figure}

@@

\begin{figure}
    \center
    \includegraphics[width=\columnwidth]{fig/pholdtree_sequential_dn.eps}
    \caption{Effect of hierarchy in sequential simulation.}
    \label{fig:PHoldtree_seq_dn_benchmark}
\end{figure}

@@

   \includegraphics[width=\columnwidth]{fig/pholdtree_alloc_BF.pdf}
   \caption{PholdTree model breadth first allocation with 4 kernels.}
   \label{fig:PholdTree_model_bfs}
   \includegraphics[width=\columnwidth]{fig/pholdtree_alloc_DF.pdf}
   \caption{PholdTree model depth first allocation with 4 kernels.}
   \label{fig:PholdTree_model_dfs}
\end{figure}

@@

\begin{figure}
    \center
    \includegraphics[width=\columnwidth]{fig/pholdtreed1n3t5000c4BFS.eps}
    \caption{Visualization of a PholdTree simulation with breadth first allocation and 4 kernels.}
    \label{fig:pholdtree_visualize_parBFS}
\end{figure}
\begin{figure}
    \center
    \includegraphics[width=\columnwidth]{fig/pholdtreed1n3t5000c4DFS.eps}
    \caption{Visualization of a PholdTree simulation with depth first allocation and 4 kernels.}
    \label{fig:pholdtree_visualize_parDFS}
\end{figure}

@@

\begin{figure}
    \center
    \includegraphics[width=\columnwidth]{fig/pholdtreeallochighp.eps}
    \caption{PholdTree model performance using different allocation schemes.}
    \label{fig:PholdTree_plot_alloc_high}
\end{figure}

### 2016-06-29 publications/Journal/4b-hotswap.tex
Save some space by putting figures next to each other
Fixed figures for twocolumn

\begin{figure}
    \center
    \includegraphics[width=\modelfraction\columnwidth, height=8cm, keepaspectratio, angle=-90 ]{fig/queue_allocation.eps}
    \caption{Queue model (d=2, w=7, t=5000, random timeadvance) allocation and simulation trace across 4 kernels.}
    \label{fig:Queue_allocation}
\end{figure}
\begin{figure}
    \center
    \includegraphics[width=\plotfraction\columnwidth]{fig/interconnect_parallel_allocation.eps}
    \caption{Interconnect parallel simulation trace for 6 models on 3 kernels.}
    \label{fig:interconnect_allocation_parallel}
\end{figure}
\begin{figure}
    \center
    \includegraphics[width=\plotfraction\columnwidth]{fig/phold_parallel_allocation.eps}
    \caption{Phold benchmark trace for parallel simulation using three kernels.}
    \label{fig:phold_allocation}
\end{figure}

>>>>

\begin{figure*}
    \center
    \includegraphics[height=\textwidth, angle=-90 ]{fig/queue_allocation.eps}
    \caption{Queue model simulation trace across 4 kernels.}
    \label{fig:Queue_allocation}
\end{figure*}
\begin{figure}
    \center
    \includegraphics[width=\plotfraction\columnwidth]{fig/interconnect_parallel_allocation.eps}
    \caption{Interconnect simulation trace for 6 models on 3 kernels.}
    \label{fig:interconnect_allocation_parallel}
\end{figure}
\begin{figure}
    \center
    \includegraphics[width=\plotfraction\columnwidth]{fig/phold_parallel_allocation.eps}
    \caption{Phold simulation trace for parallel simulation using three kernels.}
    \label{fig:phold_allocation}
\end{figure}

### 2016-06-29 publications/Journal/parallel-performance.tex
Fixed figures for twocolumn

	\includegraphics[width=\modelfraction\columnwidth]{fig/queue_fixed_weak_speedup.eps}
	\caption{Queue model weak scaling speedup compared to dxex sequential.}
	\label{fig:Queue_plot_weak}

	\includegraphics[width=\modelfraction\columnwidth]{fig/queue_fixed_strong_speedup.eps}
	\caption{Queue model strong scaling speedup compared to dxex sequential.}
	\label{fig:Queue_plot_strong}

@@

\begin{figure}
	\center
	\includegraphics[width=\plotfraction\columnwidth]{fig/interconnect_parallel.eps}
	\caption{Interconnect benchmark results for parallel simulation.}
	\label{fig:interconnect_benchmark_parallel}
\end{figure}
\begin{figure}
	\center
	\includegraphics[width=\plotfraction\columnwidth]{fig/interconnect_parallel_allocation.eps}
	\caption{Interconnect parallel simulation trace for 6 models on 3 kernels.}
	\label{fig:interconnect_allocation_parallel}
\end{figure}

@@

\begin{figure}
    \center
    \includegraphics[width=\plotfraction\columnwidth]{fig/phold_remotes.eps}
    \caption{Phold benchmark results for parallel simulation using four kernels, four atomics per node, with varying percentage of remote events.}
\end{figure}
\begin{figure}
	\center
	\includegraphics[width=\plotfraction\columnwidth]{fig/phold_priority.eps}
	\caption{Phold benchmark results for parallel simulation using four kernels, with varying amount of high-priority events.}
	\label{fig:phold_priority}
\end{figure}

>>>>

	\includegraphics[width=\columnwidth]{fig/queue_fixed_weak_speedup.eps}
	\caption{Queue model weak scaling speedup compared to dxex sequential.}
	\label{fig:Queue_plot_weak}

	\includegraphics[width=\columnwidth]{fig/queue_fixed_strong_speedup.eps}
	\caption{Queue model strong scaling speedup compared to dxex sequential.}
	\label{fig:Queue_plot_strong}

@@

\begin{figure}
	\center
	\includegraphics[width=\columnwidth]{fig/interconnect_parallel.eps}
	\caption{Interconnect benchmark results for parallel simulation.}
	\label{fig:interconnect_benchmark_parallel}
\end{figure}
\begin{figure}
	\center
	\includegraphics[width=\columnwidth]{fig/interconnect_parallel_allocation.eps}
	\caption{Interconnect parallel simulation trace for 6 models on 3 kernels.}
	\label{fig:interconnect_allocation_parallel}
\end{figure}

@@

\begin{figure}
    \center
    \includegraphics[width=\columnwidth]{fig/phold_remotes.eps}
    \caption{Phold benchmark results for parallel simulation using four kernels, four atomics per node, with varying percentage of remote events.}
\end{figure}
\begin{figure}
	\center
	\includegraphics[width=\columnwidth]{fig/phold_priority.eps}
	\caption{Phold benchmark results for parallel simulation using four kernels, with varying amount of high-priority events.}
	\label{fig:phold_priority}
\end{figure}
